---
title: "Dac summary 01/19/2021"
author: "Erica Baller"
date: "9/29/2021"
output:
  pdf_document: default
  html_document: default
---

title: "Dac Summary"
output:
  html_document: default
  pdf_document: default
---

## Dac summary

Welcome to the MS project! This is a really exciting project dedicated to understanding psychopathology, particular depression in patients with MS. It is unqiue in a variety of ways, primarily that it uses clinical images that are research grade.

The team so far is big.
PIs- Ted Satterthwaite and Taki Shinohara
Senior Scientists - Azeez Adebimpe and Matt Cieslak
Research Specialist- Timothy Robert-Fitzgerald
Graduate students - Melissa Martin
Data Analysist - Sidney Covitz
Collaborators - Aaron Alexander-Bloch and Jenna Young
DAC Pull done by - Victoria Rautman(2020/2021) and Sunil Thomas (2018)

Date of FINAL Pull: 1/19/2021
Spreadsheet: /Users/eballer/BBL/msdepression/data/dac/investigatingdepressioninmspatients_dates_right_format.csv 
Summary of request to Victoria @ DAC:
---
9/2/2020

DAC Request
Non-funded IRB Approved Research  (enter IRB number): 843669
Criteria	Display?	Description / Exclusions / Limitations / Filters
MRN	Y	Unique identifier requested, but can be masked MRN
Visit ID	Y	
Patient Class(es)
Please select only which class(es) you will need.		x  Inpatient
 X   Outpatient
x  Emergency
Age or DOB ranges	Y	
Gender	Y	
Race	Y	
Department(s)
Provide department numbers not just names.	N	
Provider(s)
Provide ID’s not just names.	N	
Date(s)
Include in the specific range and date types (eg, admit, order, result)	1/1/2010-
12/31/20	All scans based on date of first treatment with glatiramer acetate
Procedure
Please include the specific procedure codes.  (ICD9/ICD10 is preferred for inpatient)	Y	88.91 (Magnetic Resonance Imaging of Brain)

Diagnosis
Please include the specific ICD-9/ICD-10 codes including all decimal points. Do not simply include ranges or wildcards.	Y	Multiple sclerosis (ICD-9: 340; ICD-10: G35), Depressive disorders (ICD-9: 296.99, 296.21, 296.22, 296.23, 296.24, 296.25, 296.26, 296.20, 296.31, 296.32, 296.33, 296.34, 296.35, 296.26, 296.30, 300.4, 293.83, 311, ICD-10: F32.0, F32.1, F32.2, F32.3, F32.4, F32.5, F32.6, F33.0, F33.1, F33.2, F33.41, F33.42, F33.9, F34.1, F06.31, F06.32, F06.34, F32.8, F32.9, major depressive disorder, persistent depressive disorder, depressive disorder due to another medical condition, other specified depressive disorder, unspecified depressive disorder)
Orders	N	
Medication
Please list as it is ordered within the UPHS EMR’s – medication id’s preferred	Y	Glatiramer Acetate (Copaxone)
Lab Result
Please list the lab as it is ordered within the UPHS EMR’s.	Y	
Other	Y	EDSS scores (if present)
Other	Y	All medications patients are receiving
Other	Y	All PACS accession numbers available
Other	Y	PHQ-2 and PHQ-9 if present
---
9/16/2020:
Per her note to me: We also specified that we wanted to pull images with ORIG_CPT values of 70551, 70552, 70553, MHDI, IMGMR0128, and we wanted scans with department ID 361, 547, 6004, or 6013. And I may have mentioned this before but the ICD9 and ICD10 codes for MS patients are 340 and G35, respectively
 
*For us, we are additionally interested in ALL ICD9/10 codes, ALL medications they are on at the time of scan, specific labs (as indicated), EDSS , PHQ-9 and 2 scores. The particular reason for this is that we are going to be looking at the relationship of brain imaging to depression in the MS group.

Mock columns: DE_PAT_ID	PAT_ID	EMPI	HUP_MRN	PAT_NM_WMRN	SEX	RACE	ETHNIC_GROUP	ORDER_ID	ORDERING_DTTM	BEGIN_EXAM_DTTM	END_EXAM_DTTM	TECH_USER_ID	TECHNOLOGIST	ACCESSION_NUM	PROC_ID	PROC_NAME	PROC_CODE	ORIG_CPT	PERFORMING_CSN_ID	COVERAGE_ID	FIN_CLASS_NAME	VISIT_EPM_ID	PERFORMING_DEP_ID	DEPARTMENT_NAME	MODALITY	ASSOCIATED_ICD9	ASSOCIATED_ICD10	PAT_AGE_AT_EXAM	MRI_ENC_AGE	CURRENT_AGE	All ICD-9 or 10 codes	All medication codes	wbc	rbc	hemoglobin	csf studies…	phq-9 score (and date)	phq-2 score (and date)	b12	folate 	TSH	RPR Vit D



---
 1/8/2021 email update (me to Victoria Rautman):
 What we realized is that the best way to define inclusion for the MS group is to focus on people who were seen at some point in neurology clinic.
 
If you’d be so kind, I’d be grateful for *hopefully the last pull. We would use the previous one, but instead of using the ICD 9/10 codes associated with the actual scan, we would use the location of clinic visits, and pull ALL scans, before or after diagnosis.

New updates:
 -Pull all the scans for patients who have ever been seen by “NEUROLOGY SOUTH PAVILLION” and “NEUROLOGY HUP” departments for clinic. 
 
-Please include provider name associated with these department visits. 
 
-Don’t worry about doing exclusions based on ICD9/10 codes for the scans themselves, please include all and we will sort through it ourselves
 
***Please also include vitamin D levels in addition to other labs***
 
The rest of the query would be the same as the most recent query you sent back.
---

Radiology sent images to Taki and group 4/2021

This script goes through data that has been returned from the DAC on 1/19 and summarizes it
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(visreg)
library(lme4)
library(lmerTest)
library(ggplot2)
#functions
source("~/BBL/msdepression/scripts/msdepression_functions.R")
```


```{r summary}
#preprocessing - because these are sent 


#load our df

#from Jan 2021 pull
data <- read.csv("/Users/eballer/BBL/msdepression/data/dac/investigatingdepressioninmspatients_dates_right_format.csv", header = TRUE, stringsAsFactors = FALSE, na.strings = c("NULL"), sep =",")

ms_providers <- c("MARKOWITZ, CLYDE E.", "JACOBS, DINA A.", "WILLIAMSON, ERIC MICHAEL-LEE", "BERGER, JOSEPH ROBERT", "BERGER DO, JOSEPH", "PRUITT, AMY A.", "KOLSON, DENNIS L.", "CHAHIN, SALIM", "NARULA, SONA", "BAR-OR, AMIT")


#keep people with MS providers 
data_empi_acc_f_phq <- data[which(data$Provider %in% ms_providers),] #n = 17067

#keep people with ICD10 code G35 (this is the same # as people with IC9 - 340)
data_empi_acc_f_phq <- data_empi_acc_f_phq[grep("G35", data_empi_acc_f_phq$ICD10),] #n = 16830
table(data_empi_acc_f_phq$Provider)

##########################
### some preprocessing ###
##########################

#make accession # and lab findings into integer type, contained in row 28:42, Margin=2 to work on columns
data_empi_acc_f_phq$ACCESSION_NUM <- as.integer(data_empi_acc_f_phq$ACCESSION_NUM)
data_empi_acc_f_phq[27:29] <- apply(X = data_empi_acc_f_phq[27:29], FUN = as.integer, MARGIN = 2)
data_empi_acc_f_phq[31:45] <- apply(X = data_empi_acc_f_phq[31:45], FUN = as.integer, MARGIN = 2)
data_empi_acc_f_phq$sex_binarized <- ifelse(data_empi_acc_f_phq$SEX == "MALE", 1, 2)
data_empi_acc_f_phq$race_binarized <- ifelse(data_empi_acc_f_phq$RACE == "WHITE", 1, 2)
#get date into better format
data_empi_acc_f_phq$EXAM_DATE <- as.Date(data_empi_acc_f_phq$BEGIN_EXAM_DTTM, format = "%m/%d/%y")
data_empi_acc_f_phq$EXAM_DATE <- as.numeric(gsub(data_empi_acc_f_phq$EXAM_DATE, pattern = "-", replacement = ""))
########################################
#### Start counting / making subsets ###
########################################

# number of unique scanners and scans
print(paste0("Number of unique procedure names (ie. MRI Head w/out contrast; MRI Source Images): ",  length(unique(data_empi_acc_f_phq$PROC_CODE)))) #n = 10
print(paste0("Number of unique department names (ie. RAD HUP PCAM Ground): ",  length(unique(data_empi_acc_f_phq$DEPARTMENT_NAME)))) #n = 3
print(paste0("Number of unique modalities (ie. HUP PCAM GR MR4 3T; MR6 3T): ",  length(unique(data_empi_acc_f_phq$MODALITY)))) #n = 11
print(paste0("Number of unique accession #s n= ", length(unique(data_empi_acc_f_phq$ACCESSION_NUM)))) # n = 16830
print(paste0("Number of unique EMPIS n = ", length(unique(data_empi_acc_f_phq$EMPI)))) #n = 3737

#### PHQ-2 and PHQ-9 summaries

#looking at just people with phq-2 and 9
phq2_subset <- data_empi_acc_f_phq[which(!is.na(data_empi_acc_f_phq$PHQ.2)),] #n=4606

phq9_subset <- data_empi_acc_f_phq[which(!is.na(data_empi_acc_f_phq$PHQ.9)),] #n= 261

#phq-2;
print(paste0("N PHQ-2 = ", sum(!is.na(data_empi_acc_f_phq$PHQ.2)), "; n = ", length(which(phq2_subset$PHQ.2 >= 3)), " meeting criteria for depression (PHQ2) >= 3")) #n = 4606

#phq-9
print(paste0("N PHQ-9 = ", sum(!is.na(data_empi_acc_f_phq$PHQ.9)), "; noDep/mild/mod/mod-severe/severe = ", 
             length(which(phq9_subset$PHQ.9 < 5)), "/",
             length(which(phq9_subset$PHQ.9 >= 5 & phq9_subset$PHQ.9 < 10)), "/",
             length(which(phq9_subset$PHQ.9 >= 10 & phq9_subset$PHQ.9 < 15)), "/",
             length(which(phq9_subset$PHQ.9 >= 15 & phq9_subset$PHQ.9 < 20)), "/",
             length(which(phq9_subset$PHQ.9 >= 20)))) #n = 261

#both phq2 and 9

num_both_phq2_and_9 <- length(which(!is.na(data_empi_acc_f_phq$PHQ.2) & !is.na(data_empi_acc_f_phq$PHQ.9)))
print(paste0("num people with both phq2 and 9 = ", num_both_phq2_and_9)) #n = 0



#Number of unique EMPIs in phq2/phq9 subsets
unique_phq2_empis <- length(unique(phq2_subset$EMPI)) #n=966
print(paste0("N with phq2 (Unique EMPI) n = ", unique_phq2_empis, " out of ", dim(phq2_subset)[1], "; n - ", length(unique(phq2_subset$EMPI[phq2_subset$PHQ.2 >= 3])), " meeting criteria for depression (PHQ2) >= 3")) #n = 4606

unique_phq9_empis <- length(unique(phq9_subset$EMPI)) #n=76
print(paste0("N with phq9 (Unique EMPI) n = ", unique_phq9_empis, " out of ", dim(phq9_subset)[1], "; noDep/mild/mod/mod-severe/severe = ", 
             length(unique(phq9_subset$EMPI[phq9_subset$PHQ.9 < 5])), "/",
             length(unique(phq9_subset$EMPI[(phq9_subset$PHQ.9 >= 5 & phq9_subset$PHQ.9 < 10)])), "/",
             length(unique(phq9_subset$EMPI[(phq9_subset$PHQ.9 >= 10 & phq9_subset$PHQ.9 < 15)])), "/",
             length(unique(phq9_subset$EMPI[(phq9_subset$PHQ.9 >= 15 & phq9_subset$PHQ.9 < 20)])), "/",
             length(unique(phq9_subset$EMPI[phq9_subset$PHQ.9 >= 20]))))


#### ICD 9/10 for Depression
dep_df <- data_empi_acc_f_phq[grep("F3", data_empi_acc_f_phq$ICD10),] #n = 2123
num_depression <- dim(dep_df)[1]
unique_empi <- which(unique(data_empi_acc_f_phq$EMPI) %in% data_empi_acc_f_phq$EMPI) #index of the locations of unique empis; n = 3885
num_unique_EMPI_and_dep <- length(unique(dep_df$EMPI)) #n = 493

print(paste0("N with ICD 9/10 codes for depression = ", num_depression))

print(paste0("N with ICD 9/10 codes for depression and unique EMPI = ", num_unique_EMPI_and_dep, " out of ", dim(data_empi_acc_f_phq)[1]))

##### PHQ2 or 9 + ICD 9/10 Depression
num_phq2_and_dep <- length(which(!is.na(dep_df$PHQ.2))) #n = 960
print(paste0("N with ICD 9/10 codes for depression and phq2 (ALL SCANS) = ", num_phq2_and_dep, " out of ", dim(dep_df)[1]))

num_phq9_and_dep <- length(which(!is.na(dep_df$PHQ.9))) #n=140
print(paste0("N with ICD 9/10 codes for depression and phq9 (ALL SCANS) = ", num_phq9_and_dep, " out of ", dim(dep_df)[1]))

#phq-2;
print(paste0("N dep + PHQ-2 = ", sum(!is.na(dep_df$PHQ.2)), "; n = ", length(which(dep_df$PHQ.2 >= 3)), " meeting criteria for depression (PHQ2) >= 3")) #n = 4606

print(paste0("Mean dep + PHQ-2 = ", round(mean(!is.na(dep_df$PHQ.2)),3), "[",round(sd(!is.na(dep_df$PHQ.2)),3), "]; n = ", length(which(dep_df$PHQ.2 >= 3)), " meeting criteria for depression (PHQ2) >= 3")) #n = 79 

#phq-9
print(paste0("N dep + PHQ-9 = ", sum(!is.na(dep_df$PHQ.9)), "; noDep/mild/mod/mod-severe/severe = ", 
             length(which(dep_df$PHQ.9 < 5)), "/",
             length(which(dep_df$PHQ.9 >= 5 & dep_df$PHQ.9 < 10)), "/",
             length(which(dep_df$PHQ.9 >= 10 & dep_df$PHQ.9 < 15)), "/",
             length(which(dep_df$PHQ.9 >= 15 & dep_df$PHQ.9 < 20)), "/",
             length(which(dep_df$PHQ.9 >= 20)))) #n = 261

print(paste0("Mean dep + PHQ-9 = ", round(mean(!is.na(dep_df$PHQ.9)),3), "[",round(sd(!is.na(dep_df$PHQ.9)),3), "]; n = ", length(which(dep_df$PHQ.9 >= 10)), " meeting criteria for depression (PHQ9) >= 10")) #n = 79 


#### # unique people with dep dx and phq2/9 -> working on this
dep_dx_phq2_unique <- length(unique(dep_df$EMPI[!is.na(dep_df$PHQ.2)])) #n = 201
print(paste0("N with ICD 9/10 codes for depression and phq2 (unique) = ", dep_dx_phq2_unique, " out of ", dim(dep_df)[1]))

dep_dx_phq9_unique <- length(unique(dep_df$EMPI[!is.na(dep_df$PHQ.9)])) #n = 43
print(paste0("N with ICD 9/10 codes for depression and phq9 (unique) = ", dep_dx_phq9_unique, " out of ", dim(dep_df)[1]))

####


#### ICD 9/10 for Healthy Group
healthy_df <- data_empi_acc_f_phq[(-grep("F3", data_empi_acc_f_phq$ICD10)),] #n = 14707
num_healthy <- dim(healthy_df)[1]
unique_empi <- which(unique(healthy_df$EMPI) %in% healthy_df$EMPI) #index of the locations of unique empis; n = 3244
num_unique_EMPI_and_healthy <- length(unique(healthy_df$EMPI)) #n = 3244

print(paste0("N without Depression/ICD 9/10 codes for healthy = ", num_healthy))

print(paste0("N without Depression/ ICD 9/10 codes for healthy and unique EMPI = ", num_unique_EMPI_and_healthy, " out of ", dim(healthy_df)[1]))

##### PHQ2 or 9 + No Depression ICD9/10
num_phq2_and_healthy <- length(which(!is.na(healthy_df$PHQ.2))) #n = 3646
print(paste0("N without Depression/ ICD 9/10 codes for healthy and phq2 (ALL SCANS) = ", num_phq2_and_healthy, " out of ", dim(healthy_df)[1]))

#phq-2;
print(paste0("N healthy w/PHQ-2 = ", sum(!is.na(healthy_df$PHQ.2)), "; n = ", length(which(healthy_df$PHQ.2 >= 3)), " meeting criteria for depression (PHQ2) >= 3")) #n = 47

print(paste0("Mean/SD healthy w/PHQ-2 = ", round(mean(!is.na(healthy_df$PHQ.2)),3), "[",round(sd(!is.na(healthy_df$PHQ.2)),3), "]; n = ", length(which(healthy_df$PHQ.2>= 3)), " meeting criteria for depression (PHQ2) >= 3")) 


num_phq9_and_healthy <- length(which(!is.na(healthy_df$PHQ.9))) #n=121
print(paste0("N without Depression/ ICD 9/10 codes for healthy and phq9 (ALL SCANS) = ", num_phq9_and_healthy, " out of ", dim(healthy_df)[1]))


#phq-9
print(paste0("N healthy w/PHQ-9 = ", sum(!is.na(healthy_df$PHQ.9)), "; noDep/mild/mod/mod-severe/severe = ", 
             length(which(healthy_df$PHQ.9 < 5)), "/",
             length(which(healthy_df$PHQ.9 >= 5 & healthy_df$PHQ.9 < 10)), "/",
             length(which(healthy_df$PHQ.9 >= 10 & healthy_df$PHQ.9 < 15)), "/",
             length(which(healthy_df$PHQ.9 >= 15 & healthy_df$PHQ.9 < 20)), "/",
             length(which(healthy_df$PHQ.9 >= 20)))) #n = 55/34/21/1/10

print(paste0("Mean/SD healthy w/PHQ-9 = ", round(mean(!is.na(healthy_df$PHQ.9)),3), "[",round(sd(!is.na(healthy_df$PHQ.9)),3), "]; n = ", length(which(healthy_df$PHQ.9>= 10)), " meeting criteria for depression (PHQ9) >= 10")) 

#statistical testing
t.test(!is.na(healthy_df$PHQ.2), !is.na(dep_df$PHQ.2))
t.test(!is.na(healthy_df$PHQ.9), !is.na(dep_df$PHQ.9))

#test first instance of phq2/9
df_unique_empi_healthy <- healthy_df %>% 
 group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice(1) %>% 
  ungroup()

df_unique_empi_dep <- dep_df %>% 
  group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice(1) %>% 
  ungroup()

t.test(!is.na(df_unique_empi_healthy$PHQ.2), !is.na(df_unique_empi_dep$PHQ.2))
t.test(!is.na(df_unique_empi_healthy$PHQ.9), !is.na(df_unique_empi_dep$PHQ.9))

print(paste0("Mean/SD depressed w/PHQ-2/9; healthy w/ph2/9 = ",
             round(mean(!is.na(df_unique_empi_dep$PHQ.2)),3),"[",round(sd(!is.na(df_unique_empi_dep$PHQ.2)),3), "];", 
             round(mean(!is.na(df_unique_empi_dep$PHQ.9)),3),
              "[",round(sd(!is.na(df_unique_empi_dep$PHQ.9)),3), "];",
             round(mean(!is.na(df_unique_empi_healthy$PHQ.2)),3),
             "[",round(sd(!is.na(df_unique_empi_healthy$PHQ.2)),3), "];",
             round(mean(!is.na(df_unique_empi_healthy$PHQ.9)),3),
             "[",round(sd(!is.na(df_unique_empi_healthy$PHQ.9)),3), "]"))
             
             
             

#### # unique people without dep dx and phq2/9 
dep_dx_phq2_unique <- length(unique(healthy_df$EMPI[!is.na(healthy_df$PHQ.2)])) #n = 201
print(paste0("N without Depression/ ICD 9/10 codes for healthy and phq2 (unique) = ", dep_dx_phq2_unique, " out of ", dim(healthy_df)[1]))

dep_dx_phq9_unique <- length(unique(healthy_df$EMPI[!is.na(healthy_df$PHQ.9)])) #n = 43
print(paste0("N without Depression/ ICD 9/10 codes for healthy and phq9 (unique) = ", dep_dx_phq9_unique, " out of ", dim(healthy_df)[1]))

####

#demographics and lab historgrams
#print histogram of phq-2/9s for people

hist(data_empi_acc_f_phq$PHQ.2[which(!is.na(data_empi_acc_f_phq$PHQ.2))], main = paste0("PHQ-2 Histo : n = ", length(which(!is.na(data_empi_acc_f_phq$PHQ.2)))), xlab = "PHQ-2", breaks = 8)

hist(data_empi_acc_f_phq$PHQ.9[which(!is.na(data_empi_acc_f_phq$PHQ.9))], main = paste0("PHQ-9 Histo : n = ", length(which(!is.na(data_empi_acc_f_phq$PHQ.9)))), xlab = "PHQ-9", breaks = 30)

#fcode histos
hist(dep_df$PHQ.2, main = paste0("PHQ2 and Dep Histo : n = ", num_phq2_and_dep), xlab = paste0("PHQ2"))

hist(dep_df$PHQ.9,main = paste0("PHQ9 and Dep Histo : n = ", num_phq9_and_dep), xlab = paste0("PHQ9"))

###

#age histogram
hist(data_empi_acc_f_phq$MRI_ENC_AGE[which(!is.na(data_empi_acc_f_phq$MRI_ENC_AGE))], main = paste0("Age Histo : n = ", length(which(!is.na(data_empi_acc_f_phq$MRI_ENC_AGE)))), xlab = "AGE AT MRI ENCOUNTER")

#tsh
hist(data_empi_acc_f_phq$TSH[which(!is.na(data_empi_acc_f_phq$TSH))], main = paste0("TSH Histo : n = ", length(which(!is.na(data_empi_acc_f_phq$TSH)))), xlab = "TSH")

#hemoglobin
hist(data_empi_acc_f_phq$hemoglobin[which(!is.na(data_empi_acc_f_phq$hemoglobin))], main = paste0("Hemoglobin Histo : n = ", length(which(!is.na(data_empi_acc_f_phq$hemoglobin)))), xlab = "hemoglobin")

#wbc
hist(data_empi_acc_f_phq$WBC[which(!is.na(data_empi_acc_f_phq$WBC))], main = paste0("WBC Histo : n = ", length(which(!is.na(data_empi_acc_f_phq$WBC)))), xlab = "WBC")

#folate
hist(data_empi_acc_f_phq$FOLATE[which(!is.na(data_empi_acc_f_phq$FOLATE))], main = paste0("Folate Histo : n = ", length(which(!is.na(data_empi_acc_f_phq$FOLATE)))), xlab = "folate", breaks = 10)

#vitamin D
hist(data_empi_acc_f_phq$VitD[which(!is.na(data_empi_acc_f_phq$VitD))], main = paste0("Vitamin D Histo : n = ", length(which(!is.na(data_empi_acc_f_phq$VitD)))), xlab = "Vitamin D", breaks = 10)




#race
hist(data_empi_acc_f_phq$race_binarized[which(!is.na(data_empi_acc_f_phq$race_binarized))], 
     main = paste0("Race Histo : n = ", length(which(!is.na(data_empi_acc_f_phq$race))), "; White = ", length(which(data_empi_acc_f_phq$race_binarized == 1)), "; NW = ", length(which(data_empi_acc_f_phq$race_binarized == 2))),
     xlab = "white = 1, other = 2", 
     breaks = 2)

#f-codes - people usually have BOTH icd9/10 or neither

#Gender breakdown
#sex
hist(data_empi_acc_f_phq$sex_binarized[which(!is.na(data_empi_acc_f_phq$sex_binarized))], 
     main = paste0("Sex Histo : n = ", length(which(!is.na(data_empi_acc_f_phq$sex_binarized))), "; M = ", length(which(data_empi_acc_f_phq$sex_binarized == 1)), "; F = ", length(which(data_empi_acc_f_phq$sex_binarized == 2)) ), 
     xlab = "Male = 1, Female = 2", 
     breaks = 2)

#sex with depression diagnosis
hist(dep_df$sex_binarized[which(!is.na(dep_df$sex_binarized))], 
     main = paste0("Sex Histo in ICD9/10 depression dx group : n = ", length(which(!is.na(dep_df$sex_binarized))), "; M = ", length(which(dep_df$sex_binarized == 1)), "; F = ", length(which(dep_df$sex_binarized == 2)) ), 
     xlab = "Male = 1, Female = 2", 
     breaks = 2)

#sex w/ phq2
hist(phq2_subset$sex_binarized[which(!is.na(phq2_subset$sex_binarized))], 
     main = paste0("Sex Histo w/phq2: n = ", length(which(!is.na(phq2_subset$sex_binarized))), "; M = ", length(which(phq2_subset$sex_binarized == 1)), "; F = ", length(which(phq2_subset$sex_binarized == 2)) ), 
     xlab = "Male = 1, Female = 2", 
     breaks = 2)

#sex w/phq9
hist(phq9_subset$sex_binarized[which(!is.na(phq9_subset$sex_binarized))], 
     main = paste0("Sex Histo w/phq9: n = ", length(which(!is.na(phq9_subset$sex_binarized))), "; M = ", length(which(phq9_subset$sex_binarized == 1)), "; F = ", length(which(phq9_subset$sex_binarized == 2)) ), 
     xlab = "Male = 1, Female = 2", 
     breaks = 2)

```

```{r frequencies_of_dep_in_phq2_vs_9}
num_dep_phq2 <- length(which(!is.na(data_empi_acc_f_phq$PHQ.2) & (data_empi_acc_f_phq$PHQ.2 >= 3))) #n = 130
num_dep_phq9 <- length(which(!is.na(data_empi_acc_f_phq$PHQ.9) & (data_empi_acc_f_phq$PHQ.9 >= 5))) #n = 184;
#https://www.sciencedirect.com/science/article/pii/B9780128179338000293 recommends using cut point of 11
num_total_phq2 <-length(which(!is.na(data_empi_acc_f_phq$PHQ.2)))
num_total_phq9 <-length(which(!is.na(data_empi_acc_f_phq$PHQ.9))) 
dep_total_phq_table <- data.frame(matrix(data = c(num_dep_phq2, num_dep_phq9, num_total_phq2, num_total_phq9), nrow = 2, ncol = 2))
names(dep_total_phq_table) <- c("dep", "healthy")
row.names(dep_total_phq_table) <- c("phq2", "phq9")
chisq_dep_phq2_v_phq9 <- chisq.test(dep_total_phq_table)
chisq_dep_phq2_v_phq9
print("observed")
chisq_dep_phq2_v_phq9$observed
print("expected")
chisq_dep_phq2_v_phq9$expected
print("residuals")
chisq_dep_phq2_v_phq9$residuals


```
```{r chi_sq_dep_versus_healthy_PHQ2_and_9}
num_dep_phq2 <- length(which(!is.na(dep_df$PHQ.2) & (dep_df$PHQ.2 >= 3))) #n = 83
num_dep_phq9 <- length(which(!is.na(dep_df$PHQ.9) & (dep_df$PHQ.9 >= 10))) #n = 79
num_healthy_phq2 <- length(which(!is.na(healthy_df$PHQ.2) & (healthy_df$PHQ.2 >= 3))) #n = 47
num_healthy_phq9 <- length(which(!is.na(healthy_df$PHQ.9) & (healthy_df$PHQ.9 >= 10))) #n = 32;
total_dep_phq2 <- length(which(!is.na(dep_df$PHQ.2))) #n = 83
total_dep_phq9 <- length(which(!is.na(dep_df$PHQ.9))) #n = 79
total_healthy_phq2 <- length(which(!is.na(healthy_df$PHQ.2))) #n = 47
total_healthy_phq9 <- length(which(!is.na(healthy_df$PHQ.9))) #n = 32;


#### phq2 symptomatic versus asymptomatic
phq2_table <- data.frame(matrix(data = c(num_dep_phq2,(total_dep_phq2-num_dep_phq2), num_healthy_phq2,   (total_healthy_phq2-num_healthy_phq2)), nrow = 2, ncol = 2))
names(phq2_table) <- c("dep", "healthy")
row.names(phq2_table) <- c("symptomatic", "asymptomatic")
chisq_dep_phq2 <- chisq.test(phq2_table)
chisq_dep_phq2
print("observed")
chisq_dep_phq2$observed
print("expected")
chisq_dep_phq2$expected
print("residuals")
chisq_dep_phq2$residuals

#### phq9 symptomatic versus asymptomatic
phq9_table <- data.frame(matrix(data = c(num_dep_phq9,(total_dep_phq9-num_dep_phq9), num_healthy_phq9,   (total_healthy_phq9 - num_healthy_phq9)), nrow = 2, ncol = 2))
names(phq9_table) <- c("dep", "healthy")
row.names(phq9_table) <- c("symptomatic", "asymptomatic")
chisq_dep_phq9 <- chisq.test(phq9_table)
chisq_dep_phq9
print("observed")
chisq_dep_phq9$observed
print("expected")
chisq_dep_phq9$expected
print("residuals")
chisq_dep_phq9$residuals


################### Unique 

num_dep_phq2 <- length(which(!is.na(dep_df$PHQ.2) & (dep_df$PHQ.2 >= 3))) #n = 83
num_dep_phq9 <- length(which(!is.na(dep_df$PHQ.9) & (dep_df$PHQ.9 >= 10))) #n = 79
num_healthy_phq2 <- length(which(!is.na(healthy_df$PHQ.2) & (healthy_df$PHQ.2 >= 3))) #n = 47
num_healthy_phq9 <- length(which(!is.na(healthy_df$PHQ.9) & (healthy_df$PHQ.9 >= 10))) #n = 32;
total_dep_phq2 <- length(which(!is.na(dep_df$PHQ.2))) #n = 83
total_dep_phq9 <- length(which(!is.na(dep_df$PHQ.9))) #n = 79
total_healthy_phq2 <- length(which(!is.na(healthy_df$PHQ.2))) #n = 47
total_healthy_phq9 <- length(which(!is.na(healthy_df$PHQ.9))) #n = 32;


#patients who are depressed who score on phq2/9
num_dep_phq2_unique <- length(unique(dep_df$EMPI[which(dep_df$PHQ.2 >= 3)]))
num_dep_phq9_unique <- length(unique(dep_df$EMPI[which(dep_df$PHQ.9 >= 10)]))

#persons who are characterized as healthy but score on PHQ2/9
num_healthy_phq2_unique <- length(unique(healthy_df$EMPI[which(healthy_df$PHQ.2 >= 3)]))
num_healthy_phq9_unique <- length(unique(healthy_df$EMPI[which(healthy_df$PHQ.9 >= 10)]))

#total # of people who have phq2/9
asym_dep_phq2_unique <- length(unique(dep_df$EMPI[which(!is.na(dep_df$PHQ.2))])) - num_dep_phq2_unique
asym_dep_phq9_unique <- length(unique(dep_df$EMPI[which(!is.na(dep_df$PHQ.9))])) - num_dep_phq9_unique
asym_healthy_phq2_unique <- length(unique(healthy_df$EMPI[which(!is.na(healthy_df$PHQ.2))])) - num_healthy_phq2_unique
asym_healthy_phq9_unique <- length(unique(healthy_df$EMPI[which(!is.na(healthy_df$PHQ.9))])) - num_healthy_phq9_unique 


#### phq2 symptomatic versus asymptomatic
phq2_table_unique <- data.frame(matrix(data = c(num_dep_phq2_unique,asym_dep_phq2_unique, num_healthy_phq2_unique, asym_healthy_phq2_unique), nrow = 2, ncol = 2))
names(phq2_table_unique) <- c("dep", "healthy")
row.names(phq2_table_unique) <- c("symptomatic", "asymptomatic")
chisq_dep_phq2_unique <- chisq.test(phq2_table_unique)
chisq_dep_phq2_unique
print("observed")
chisq_dep_phq2_unique$observed
print("expected")
chisq_dep_phq2_unique$expected
print("residuals")
chisq_dep_phq2_unique$residuals

#### phq9 symptomatic versus asymptomatic
phq9_table_unique <- data.frame(matrix(data = c(num_dep_phq9_unique,asym_dep_phq9_unique, num_healthy_phq9_unique,   asym_healthy_phq9_unique), nrow = 2, ncol = 2))
names(phq9_table_unique) <- c("dep", "healthy")
row.names(phq9_table_unique) <- c("symptomatic", "asymptomatic")
chisq_dep_phq9_unique <- chisq.test(phq9_table_unique)
chisq_dep_phq9_unique
print("observed")
chisq_dep_phq9_unique$observed
print("expected")
chisq_dep_phq9_unique$expected
print("residuals")
chisq_dep_phq9_unique$residuals




```

This next step, put together 9/29/2021, aims to define our control and case groups based on the following definitions-

Healthy group - No F33* code, and PHQ2 and 9 always 0

Lifetime depression - EITHER F33* diagnosis OR PHQ2 >= 3 OR PHQ9 >= 10
   - of note:
    *PHQ9 0-4 - no depression
    * 5-9 - mild depression
    * 10-14 - moderate depression
    * 15-19 - mod/severe
    * 20+ - severe
    
Logic
  1) First, separate out people with ICD10 code (F3*) into depressed and non depressed
       - dep_df is people with an F3* code
       - healthy df is people without
       - look for unique EMPIs in each of these groups
 
  2) Within "healthy" group, separate who has EVER had a lifetime history of testing positive on PHQ2 
        - Depression is PHQ2 >=3 at any point
        - Healthy if PHQ2 = 0
        - Look for unique EMPIs in these groups
 
  3) Within "healthy" group, separate who has EVER had a lifetime history of testing positive on PHQ9
        - Depression is PHQ9 >= 10 at any point
        - Healthy if PHQ9 = 0
        - Look for unique EMPIs in these groups
 
  4) Combine for depressed group and healthy
        - Look for people with PHQ2 or 9 meeting criteria for depression that aren't in depression group, and add them -> dep_num_icd10_plus_phq2_and_phq9
        - remove people from healthy_df if people had EMPIs in phq2 or 9 depressed group -> healthy_num_no_icd10_plus_phq2_and_phq9
        - make separate group that only includes healthies for whom we have phq2 or 9 -> healthy_num_no_icd10_plus_phq2_and_phq9_MUST_HAVE_PHQ2_OR_9
         
```{r defining_control_and_dep_groups}

##########################################################
#### Step 1- make F3* depressed and healthy groups* ######
##########################################################

########
### separate out depressed group
########
print("separate out depressed group")
dep_df <- data_empi_acc_f_phq[grep("F3", data_empi_acc_f_phq$ICD10),] #n = 2123
num_depression <- dim(dep_df)[1]
num_unique_EMPI_and_dep <- length(unique(dep_df$EMPI)) #n = 493
print(paste0("N with ICD 9/10 codes for depression = ", num_depression))
print(paste0("N with ICD 9/10 codes for depression and unique EMPI in whole depression group = ", num_unique_EMPI_and_dep, " out of ", num_depression))

#######
### separate out healthy group
#######
print("separate out healthy group")
healthy_df <- data_empi_acc_f_phq[-grep("F3", data_empi_acc_f_phq$ICD10),] #n = 14707
num_healthy <- dim(healthy_df)[1] 
num_unique_EMPI_and_healthy <- length(unique(healthy_df$EMPI)) #n = 3244
print(paste0("N with WITHOUT depression ICD 9/10 codes (i.e. \"healthy\"): ", num_healthy))
print(paste0("N with WITHOUT ICD 9/10 depression codes for depression and unique EMPI = ", num_unique_EMPI_and_healthy, " out of ", num_healthy))

##########################################################
#### Step 2- Identify PHQ2 >=3 in healthy group     ######
##########################################################

print("Get people in healthy group with phq2s for dep/healthy")
# num in healthy group with PHQ2
phq2_subset <- healthy_df[which(!is.na(healthy_df$PHQ.2)),] #n=3646, unique 698
depressed_phq2_subset <- phq2_subset[which(phq2_subset$PHQ.2 >= 3),] #n = 47 
depressed_unique_phq2_empis <- unique(depressed_phq2_subset$EMPI) #n=10
healthy_phq2_subset <- phq2_subset[which(phq2_subset$PHQ.2 == 0),] #n = 3326
healthy_unique_phq2_empis <- unique(healthy_phq2_subset$EMPI) #n = 631

print(paste0("PHQ2 breakdown in healthy group (total n with score = ", dim(phq2_subset)[1], "[unique = ", length(unique(phq2_subset$EMPI)),"]): PHQ2 >= 3 :", dim(depressed_phq2_subset)[1], "[unique = ", length(depressed_unique_phq2_empis), "]; PHQ2 == 0 : ", dim(healthy_phq2_subset)[1], "[unique = ", length(healthy_unique_phq2_empis),"]"))


##########################################################
#### Step 3- Identify PHQ9 >=10 in healthy group    ######
##########################################################

print("Get people in healthy group with phq9s for dep/healthy")
# num in healthy group with PHQ9
phq9_subset <- healthy_df[which(!is.na(healthy_df$PHQ.9)),] #n=121
depressed_phq9_subset <- phq9_subset[which(phq9_subset$PHQ.9 >= 10),] #n = 32 
depressed_unique_phq9_empis <- unique(depressed_phq9_subset$EMPI) #n=9
healthy_phq9_subset <- phq9_subset[which(phq9_subset$PHQ.9 == 0),] #n = 21
healthy_unique_phq9_empis <- unique(healthy_phq9_subset$EMPI) #n =4

print(paste0("PHQ9 breakdown in healthy group (total n with score = ", dim(phq9_subset)[1], "[unique = ", length(unique(phq9_subset$EMPI)),"]): PHQ9 >= 10 :", dim(depressed_phq9_subset)[1], "[unique = ", length(depressed_unique_phq9_empis), "]; PHQ9 == 0 : ", dim(healthy_phq9_subset)[1], "[unique = ", length(unique(healthy_phq9_subset$EMPI)),"]"))


##########################################################
#Step 4 - Combine for depressed group and healthy groups #
##########################################################

print("Combine groups for new cohort")
gain_in_dep_group <- length(depressed_unique_phq2_empis) + length(depressed_unique_phq9_empis)
dep_num_icd10_plus_phq2_and_phq9 <- num_unique_EMPI_and_dep + gain_in_dep_group # we can do this because we know they are each exclusive - num_unique_empi_and_dep from icd10 group, and no overlap in phq2 and 9 group
print(paste0("number of UNIQUE people with an icd10 code for Depression OR scored positive on PHQ2(>=3) or PHQ9(>=10) : ", dep_num_icd10_plus_phq2_and_phq9, ", for a gain of n = ", gain_in_dep_group))

healthy_num_no_icd10_plus_phq2_and_phq9 <- num_unique_EMPI_and_healthy - gain_in_dep_group #take number of people who don't have depression diagnosis and don't have a depression phq2/9

print(paste0("number of UNIQUE people with NO icd10 code for Depression and NEVER had a PHQ2(>=3) or PHQ9(>=10) : ", healthy_num_no_icd10_plus_phq2_and_phq9, ", for a loss of n = ", gain_in_dep_group))

healthy_num_no_icd10_plus_phq2_and_phq9_MUST_HAVE_PHQ2_OR_9 <- length(healthy_unique_phq2_empis) + length(healthy_unique_phq9_empis)
print(paste0("number of UNIQUE people with NO icd10 code for Depression and HAS HAD AT LEAST 1 PHQ2 or 9 that was 0) : ", healthy_num_no_icd10_plus_phq2_and_phq9_MUST_HAVE_PHQ2_OR_9))


print(paste0("Cleanest cohort (depressed in icd9/10 or Phq2/9; healthy by at least one phq2/9 and never depression dx ---->>>>  Depressed: ", dep_num_icd10_plus_phq2_and_phq9, "; Healthy: ", healthy_num_no_icd10_plus_phq2_and_phq9_MUST_HAVE_PHQ2_OR_9))


##### THESE ARE THE DATAFRAMES I WANT TO USE GOING FORWARD ###
#all empis for depressed group include people with depresssion dx, and people who got in for phq2 or phq9
empis_for_depressed_group <- append(
  append(unique(dep_df$EMPI), depressed_unique_phq2_empis), depressed_unique_phq9_empis)

final_depressed_group_withICD_AND_depressed_phq2_or_9 <- 
  data_empi_acc_f_phq %>%
filter(EMPI %in% empis_for_depressed_group)

#------
empis_for_healthy_group <- append(healthy_unique_phq2_empis, healthy_unique_phq9_empis)

final_healthy_group_withNOICD_AND_phq2_or_9_0<- 
  data_empi_acc_f_phq %>%
filter(EMPI %in% empis_for_healthy_group)

#------
### add a column to the original dataframe with a 0 if not in any group, -1 if healthy, and 1 if depressed
data_empi_acc_f_phq$depGroupVar = 0
data_empi_acc_f_phq$depGroupVar[which(data_empi_acc_f_phq$EMPI %in% empis_for_depressed_group)] = 1
data_empi_acc_f_phq$depGroupVar[which(data_empi_acc_f_phq$EMPI %in% empis_for_healthy_group)] = -1
data_empi_acc_f_phq$depGroupVar = as.factor(data_empi_acc_f_phq$depGroupVar)

```

```{r sex_differences_regressions}


### looking at anyone with phq2s or 9s
males.phq2 <- phq2_subset[which(phq2_subset$SEX == "MALE"),] #n = 951, mean = 0.20
females.phq2 <- phq2_subset[which(phq2_subset$SEX == "FEMALE"),] #n = 3655, mean = 0.26
m_v_f_phq2 <- t.test(males.phq2$PHQ.2, females.phq2$PHQ.2) #p = 0.03 ***

males.phq9 <- phq9_subset[which(phq9_subset$SEX == "MALE"),] #n = 80, mean = 8.63
females.phq9 <- phq9_subset[which(phq9_subset$SEX == "FEMALE"),] #n = 181, mean = 9.13
m_v_f_phq9 <- t.test(males.phq9$PHQ.9, females.phq9$PHQ.9)

#### Looking at depressed group
## interstingly, not the 2:1 ratio we usually see in general world
## phq2 means suggest people are not depressed 
## phq2 means suggest people meet criteria for mild depression

males_dep <- dep_df[(which(dep_df$SEX == "MALE")),] #n = 419/total(4087; 10%) F; mean PHQ2 = 0.61, mean PHQ9 = 13.05
females_dep <- dep_df[(which(dep_df$SEX == "FEMALE")),] #n = 1704/total(12743; 13%)total F; mean = 0.56; mean PHQ9 = 10.61
m_v_f_dep_phq2 <- t.test(males_dep$PHQ.2, females_dep$PHQ.2) #p = 0.66
m_v_f_dep_phq9 <- t.test(males_dep$PHQ.9, females_dep$PHQ.9) #p = 0.24

#chi sq comparing # of pts dx with depression in males vs females; col 1- male dep n, female dep n; col 2- male total n, female total n
### fascinating - only 12% of people even gave a dx of depression in their charts. More likely to have it if female than male; also phq2 mean only slightly higher in females. 
num_dep_m <- dim(males_dep)[1] #n = 419
num_dep_f <-  dim(females_dep)[1]#n = 1704
num_total_m <- length(which(data_empi_acc_f_phq$SEX == "MALE")) #n = 4087
num_total_f <- length(which(data_empi_acc_f_phq$SEX == "FEMALE")) #n = 
m_v_f_table <- data.frame(matrix(data = c(num_dep_m, num_dep_f, num_total_m, num_total_f), nrow = 2, ncol = 2))
names(m_v_f_table) <- c("dep", "total")
row.names(m_v_f_table) <- c("male", "female")
chisq_m_v_f_dist <- chisq.test(m_v_f_table) #p = 4 x 10^-6
chisq_m_v_f_dist
print("observed")
chisq_m_v_f_dist$observed
print("expected")
chisq_m_v_f_dist$expected
print("residuals")
chisq_m_v_f_dist$residuals
#chisq comparing # of 

```





```{r summary_psychosis}
#preprocessing - because these are sent 


#load our df

#from Jan 2021 pull
data <- read.csv("/Users/eballer/BBL/msdepression/data/dac/investigatingdepressioninmspatients_dates_right_format.csv", header = TRUE, stringsAsFactors = FALSE, na.strings = c("NULL"), sep =",")

ms_providers <- c("MARKOWITZ, CLYDE E.", "JACOBS, DINA A.", "WILLIAMSON, ERIC MICHAEL-LEE", "BERGER, JOSEPH ROBERT", "BERGER DO, JOSEPH", "PRUITT, AMY A.", "KOLSON, DENNIS L.", "CHAHIN, SALIM", "NARULA, SONA", "BAR-OR, AMIT")


#keep people with MS providers 
data_empi_acc_f_phq <- data[which(data$Provider %in% ms_providers),] #n = 17067

#keep people with ICD10 code G35 (this is the same # as people with IC9 - 340)
data_empi_acc_f_phq <- data_empi_acc_f_phq[grep("G35", data_empi_acc_f_phq$ICD10),] #n = 16830
table(data_empi_acc_f_phq$Provider)

##########################
### some preprocessing ###
##########################

#make accession # and lab findings into integer type, contained in row 28:42, Margin=2 to work on columns
data_empi_acc_f_phq$ACCESSION_NUM <- as.integer(data_empi_acc_f_phq$ACCESSION_NUM)
data_empi_acc_f_phq[27:29] <- apply(X = data_empi_acc_f_phq[27:29], FUN = as.integer, MARGIN = 2)
data_empi_acc_f_phq[31:45] <- apply(X = data_empi_acc_f_phq[31:45], FUN = as.integer, MARGIN = 2)
data_empi_acc_f_phq$sex_binarized <- ifelse(data_empi_acc_f_phq$SEX == "MALE", 1, 2)
data_empi_acc_f_phq$race_binarized <- ifelse(data_empi_acc_f_phq$RACE == "WHITE", 1, 2)

########################################
#### Start counting / making subsets ###
########################################

# number of unique scanners and scans
print(paste0("Number of unique procedure names (ie. MRI Head w/out contrast; MRI Source Images): ",  length(unique(data_empi_acc_f_phq$PROC_CODE)))) #n = 10
print(paste0("Number of unique department names (ie. RAD HUP PCAM Ground): ",  length(unique(data_empi_acc_f_phq$DEPARTMENT_NAME)))) #n = 3
print(paste0("Number of unique modalities (ie. HUP PCAM GR MR4 3T; MR6 3T): ",  length(unique(data_empi_acc_f_phq$MODALITY)))) #n = 11
print(paste0("Number of unique accession #s n= ", length(unique(data_empi_acc_f_phq$ACCESSION_NUM)))) # n = 16830
print(paste0("Number of unique EMPIS n = ", length(unique(data_empi_acc_f_phq$EMPI)))) #n = 3737

#### PHQ-2 and PHQ-9 summaries

#looking at just people with phq-2 and 9
phq2_subset <- data_empi_acc_f_phq[which(!is.na(data_empi_acc_f_phq$PHQ.2)),] #n=4606

phq9_subset <- data_empi_acc_f_phq[which(!is.na(data_empi_acc_f_phq$PHQ.9)),] #n= 261

#phq-2;
print(paste0("N PHQ-2 = ", sum(!is.na(data_empi_acc_f_phq$PHQ.2)), "; n = ", length(which(phq2_subset$PHQ.2 >= 3)), " meeting criteria for depression (PHQ2) >= 3")) #n = 4606

#phq-9
print(paste0("N PHQ-9 = ", sum(!is.na(data_empi_acc_f_phq$PHQ.9)), "; noDep/mild/mod/mod-severe/severe = ", 
             length(which(phq9_subset$PHQ.9 < 5)), "/",
             length(which(phq9_subset$PHQ.9 >= 5 & phq9_subset$PHQ.9 < 10)), "/",
             length(which(phq9_subset$PHQ.9 >= 10 & phq9_subset$PHQ.9 < 15)), "/",
             length(which(phq9_subset$PHQ.9 >= 15 & phq9_subset$PHQ.9 < 20)), "/",
             length(which(phq9_subset$PHQ.9 >= 20)))) #n = 261

#both phq2 and 9

num_both_phq2_and_9 <- length(which(!is.na(data_empi_acc_f_phq$PHQ.2) & !is.na(data_empi_acc_f_phq$PHQ.9)))
print(paste0("num people with both phq2 and 9 = ", num_both_phq2_and_9)) #n = 0



#Number of unique EMPIs in phq2/phq9 subsets
unique_phq2_empis <- length(unique(phq2_subset$EMPI)) #n=966
print(paste0("N with phq2 (Unique EMPI) n = ", unique_phq2_empis, " out of ", dim(phq2_subset)[1], "; n - ", length(unique(phq2_subset$EMPI[phq2_subset$PHQ.2 >= 3])), " meeting criteria for depression (PHQ2) >= 3")) #n = 4606

unique_phq9_empis <- length(unique(phq9_subset$EMPI)) #n=76
print(paste0("N with phq9 (Unique EMPI) n = ", unique_phq9_empis, " out of ", dim(phq9_subset)[1], "; noDep/mild/mod/mod-severe/severe = ", 
             length(unique(phq9_subset$EMPI[phq9_subset$PHQ.9 < 5])), "/",
             length(unique(phq9_subset$EMPI[(phq9_subset$PHQ.9 >= 5 & phq9_subset$PHQ.9 < 10)])), "/",
             length(unique(phq9_subset$EMPI[(phq9_subset$PHQ.9 >= 10 & phq9_subset$PHQ.9 < 15)])), "/",
             length(unique(phq9_subset$EMPI[(phq9_subset$PHQ.9 >= 15 & phq9_subset$PHQ.9 < 20)])), "/",
             length(unique(phq9_subset$EMPI[phq9_subset$PHQ.9 >= 20]))))


#### ICD 9/10 for Psychosis
psychosis_df <- data_empi_acc_f_phq[grep("F2", data_empi_acc_f_phq$ICD10),] #n = 2123
num_psychosis <- dim(psychosis_df)[1]
unique_empi <- which(unique(data_empi_acc_f_phq$EMPI) %in% data_empi_acc_f_phq$EMPI) #index of the locations of unique empis; n = 3885
num_unique_EMPI_and_psychosis <- length(unique(psychosis_df$EMPI)) #n = 493

print(paste0("N with ICD 9/10 codes for psychosis = ", num_psychosis))

print(paste0("N with ICD 9/10 codes for psychosis and unique EMPI = ", num_unique_EMPI_and_psychosis, " out of ", dim(data_empi_acc_f_phq)[1]))

##### PHQ2 or 9 + ICD 9/10 psychosis
num_phq2_and_psychosis <- length(which(!is.na(psychosis_df$PHQ.2))) #n = 960
print(paste0("N with ICD 9/10 codes for psychosis and phq2 (ALL SCANS) = ", num_phq2_and_psychosis, " out of ", dim(psychosis_df)[1]))

num_phq9_and_psychosis <- length(which(!is.na(psychosis_df$PHQ.9))) #n=140
print(paste0("N with ICD 9/10 codes for psychosis and phq9 (ALL SCANS) = ", num_phq9_and_psychosis, " out of ", dim(psychosis_df)[1]))

#phq-2;
print(paste0("N psychosis + PHQ-2 = ", sum(!is.na(psychosis_df$PHQ.2)), "; n = ", length(which(psychosis_df$PHQ.2 >= 3)), " meeting criteria for psychosis (PHQ2) >= 3")) #n = 4606

#phq-9
print(paste0("N psychosis + PHQ-9 = ", sum(!is.na(psychosis_df$PHQ.9)), "; nopsychosis/mild/mod/mod-severe/severe = ", 
             length(which(psychosis_df$PHQ.9 < 5)), "/",
             length(which(psychosis_df$PHQ.9 >= 5 & psychosis_df$PHQ.9 < 10)), "/",
             length(which(psychosis_df$PHQ.9 >= 10 & psychosis_df$PHQ.9 < 15)), "/",
             length(which(psychosis_df$PHQ.9 >= 15 & psychosis_df$PHQ.9 < 20)), "/",
             length(which(psychosis_df$PHQ.9 >= 20)))) #n = 261


#### # unique people with psychosis dx and phq2/9 -> working on this
psychosis_dx_phq2_unique <- length(unique(psychosis_df$EMPI[!is.na(psychosis_df$PHQ.2)])) #n = 201
print(paste0("N with ICD 9/10 codes for psychosis and phq2 (unique) = ", psychosis_dx_phq2_unique, " out of ", dim(psychosis_df)[1]))

psychosis_dx_phq9_unique <- length(unique(psychosis_df$EMPI[!is.na(psychosis_df$PHQ.9)])) #n = 43
print(paste0("N with ICD 9/10 codes for psychosis and phq9 (unique) = ", psychosis_dx_phq9_unique, " out of ", dim(psychosis_df)[1]))

####


#### ICD 9/10 for Healthy Group
healthy_df <- data_empi_acc_f_phq[(-grep("F3", data_empi_acc_f_phq$ICD10)),] #n = 14707
num_healthy <- dim(healthy_df)[1]
unique_empi <- which(unique(healthy_df$EMPI) %in% healthy_df$EMPI) #index of the locations of unique empis; n = 3244
num_unique_EMPI_and_healthy <- length(unique(healthy_df$EMPI)) #n = 3244

print(paste0("N without psychosis/ICD 9/10 codes for healthy = ", num_healthy))

print(paste0("N without psychosis/ ICD 9/10 codes for healthy and unique EMPI = ", num_unique_EMPI_and_healthy, " out of ", dim(healthy_df)[1]))

##### PHQ2 or 9 + No psychosis ICD9/10
num_phq2_and_healthy <- length(which(!is.na(healthy_df$PHQ.2))) #n = 3646
print(paste0("N without psychosis/ ICD 9/10 codes for healthy and phq2 (ALL SCANS) = ", num_phq2_and_healthy, " out of ", dim(healthy_df)[1]))

#phq-2;
print(paste0("N healthy w/PHQ-2 = ", sum(!is.na(healthy_df$PHQ.2)), "; n = ", length(which(healthy_df$PHQ.2 >= 3)), " meeting criteria for psychosis (PHQ2) >= 3")) #n = 47

num_phq9_and_healthy <- length(which(!is.na(healthy_df$PHQ.9))) #n=121
print(paste0("N without psychosis/ ICD 9/10 codes for healthy and phq9 (ALL SCANS) = ", num_phq9_and_healthy, " out of ", dim(healthy_df)[1]))


#phq-9
print(paste0("N healthy w/PHQ-9 = ", sum(!is.na(healthy_df$PHQ.9)), "; nopsychosis/mild/mod/mod-severe/severe = ", 
             length(which(healthy_df$PHQ.9 < 5)), "/",
             length(which(healthy_df$PHQ.9 >= 5 & healthy_df$PHQ.9 < 10)), "/",
             length(which(healthy_df$PHQ.9 >= 10 & healthy_df$PHQ.9 < 15)), "/",
             length(which(healthy_df$PHQ.9 >= 15 & healthy_df$PHQ.9 < 20)), "/",
             length(which(healthy_df$PHQ.9 >= 20)))) #n = 55/34/21/1/10


#### # unique people without psychosis dx and phq2/9 
psychosis_dx_phq2_unique <- length(unique(healthy_df$EMPI[!is.na(healthy_df$PHQ.2)])) #n = 201
print(paste0("N without psychosis/ ICD 9/10 codes for healthy and phq2 (unique) = ", psychosis_dx_phq2_unique, " out of ", dim(healthy_df)[1]))

psychosis_dx_phq9_unique <- length(unique(healthy_df$EMPI[!is.na(healthy_df$PHQ.9)])) #n = 43
print(paste0("N without psychosis/ ICD 9/10 codes for healthy and phq9 (unique) = ", psychosis_dx_phq9_unique, " out of ", dim(healthy_df)[1]))

####

#demographics and lab historgrams
#print histogram of phq-2/9s for people

hist(data_empi_acc_f_phq$PHQ.2[which(!is.na(data_empi_acc_f_phq$PHQ.2))], main = paste0("PHQ-2 Histo : n = ", length(which(!is.na(data_empi_acc_f_phq$PHQ.2)))), xlab = "PHQ-2", breaks = 8)

hist(data_empi_acc_f_phq$PHQ.9[which(!is.na(data_empi_acc_f_phq$PHQ.9))], main = paste0("PHQ-9 Histo : n = ", length(which(!is.na(data_empi_acc_f_phq$PHQ.9)))), xlab = "PHQ-9", breaks = 30)

#fcode histos - no one with it at this time. 
#hist(psychosis_df$PHQ.2, main = paste0("PHQ2 and psychosis Histo : n = ", num_phq2_and_psychosis), xlab = paste0("PHQ2"))

#hist(psychosis_df$PHQ.9,main = paste0("PHQ9 and psychosis Histo : n = ", num_phq9_and_psychosis), xlab = paste0("PHQ9"))

###

#age histogram
hist(data_empi_acc_f_phq$MRI_ENC_AGE[which(!is.na(data_empi_acc_f_phq$MRI_ENC_AGE))], main = paste0("Age Histo : n = ", length(which(!is.na(data_empi_acc_f_phq$MRI_ENC_AGE)))), xlab = "AGE AT MRI ENCOUNTER")

#tsh
hist(data_empi_acc_f_phq$TSH[which(!is.na(data_empi_acc_f_phq$TSH))], main = paste0("TSH Histo : n = ", length(which(!is.na(data_empi_acc_f_phq$TSH)))), xlab = "TSH")

#hemoglobin
hist(data_empi_acc_f_phq$hemoglobin[which(!is.na(data_empi_acc_f_phq$hemoglobin))], main = paste0("Hemoglobin Histo : n = ", length(which(!is.na(data_empi_acc_f_phq$hemoglobin)))), xlab = "hemoglobin")

#wbc
hist(data_empi_acc_f_phq$WBC[which(!is.na(data_empi_acc_f_phq$WBC))], main = paste0("WBC Histo : n = ", length(which(!is.na(data_empi_acc_f_phq$WBC)))), xlab = "WBC")

#folate
hist(data_empi_acc_f_phq$FOLATE[which(!is.na(data_empi_acc_f_phq$FOLATE))], main = paste0("Folate Histo : n = ", length(which(!is.na(data_empi_acc_f_phq$FOLATE)))), xlab = "folate", breaks = 10)

#vitamin D
hist(data_empi_acc_f_phq$VitD[which(!is.na(data_empi_acc_f_phq$VitD))], main = paste0("Vitamin D Histo : n = ", length(which(!is.na(data_empi_acc_f_phq$VitD)))), xlab = "Vitamin D", breaks = 10)




#race
hist(data_empi_acc_f_phq$race_binarized[which(!is.na(data_empi_acc_f_phq$race_binarized))], 
     main = paste0("Race Histo : n = ", length(which(!is.na(data_empi_acc_f_phq$race))), "; White = ", length(which(data_empi_acc_f_phq$race_binarized == 1)), "; NW = ", length(which(data_empi_acc_f_phq$race_binarized == 2))),
     xlab = "white = 1, other = 2", 
     breaks = 2)

#f-codes - people usually have BOTH icd9/10 or neither

#Gender breakdown
#sex
hist(data_empi_acc_f_phq$sex_binarized[which(!is.na(data_empi_acc_f_phq$sex_binarized))], 
     main = paste0("Sex Histo : n = ", length(which(!is.na(data_empi_acc_f_phq$sex_binarized))), "; M = ", length(which(data_empi_acc_f_phq$sex_binarized == 1)), "; F = ", length(which(data_empi_acc_f_phq$sex_binarized == 2)) ), 
     xlab = "Male = 1, Female = 2", 
     breaks = 2)


```


```{r comparing_out_group_with_Tim_group}
##### checking to see whether we have clinical data for patients who have already been segmented as of 5/4/2021
### had to do some parsing of tim's spreadsheet: /Users/eballer/BBL/msdepression/data/insurance_images_for_depression.csv
### used the following commands to extract the empi and the date -> in tim's they are in the format sub-***** and ses-YYYYMMDD

## more insurance_images_for_depression.csv | cut -f1 -d ','| perl -pe 's/sub-(.*)/$1/' > tim_empi
## more insurance_images_for_depression.csv | cut -f2 -d ','| perl -pe 's/ses-(....)(..)(..)/$2\/$3\/$1/' > tim_dates
## more tim_dates | perl -pe 's/(.*)20(..)/$1$2/' | perl -pe 's/(0)(.)\/(.*)\/(.*)/$2\/$3\/$4/' | perl -pe 's/(.*)\/(0)(.*)\/(.*)/$1\/$3\/$4/' > tim_dates_no_zero_pad

#segmented <- read.csv("/Users/eballer/BBL/msdepression/data/insurance_images_for_depression_with_accession.csv", header = F, sep = ",") #n = 4468
segmented <- read.csv("/Users/eballer/BBL/msdepression/data/insurance_images_for_depression3.csv", header = F, sep = ",") #n = 2833

names(segmented) <- c("EMPI", "EXAM_DATE", "SES", "ACCESSION_NUM")


#look at the overlap of EMPIs. Won't be able to actually check the matching of scan to person without either accession #s or changing the format of the date. 
number_of_people_in_tims_group_that_are_also_in_mine <- length(which(segmented$ACCESSION_NUM %in% data_empi_acc_f_phq$ACCESSION_NUM)) #2919
overlap_group <- data_empi_acc_f_phq[which(data_empi_acc_f_phq$ACCESSION_NUM %in% segmented$ACCESSION_NUM),]

print(paste0("Num people in previously curated group and Erica's group -> ", dim(overlap_group)[1]))

#### PHQ-2 and PHQ-9 summaries

#looking at just people with phq-2 and 9
phq2_subset <- overlap_group[which(!is.na(overlap_group$PHQ.2)),] #n=4606

phq9_subset <- overlap_group[which(!is.na(overlap_group$PHQ.9)),] #n= 261

#phq-2;
print(paste0("N PHQ-2 = ", sum(!is.na(overlap_group$PHQ.2)), "; n = ", length(which(phq2_subset$PHQ.2 >= 3)), " meeting criteria for depression (PHQ2) >= 3")) #n = 4606

#phq-9
print(paste0("N PHQ-9 = ", sum(!is.na(overlap_group$PHQ.9)), "; noDep/mild/mod/mod-severe/severe = ", 
             length(which(phq9_subset$PHQ.9 < 5)), "/",
             length(which(phq9_subset$PHQ.9 >= 5 & phq9_subset$PHQ.9 < 10)), "/",
             length(which(phq9_subset$PHQ.9 >= 10 & phq9_subset$PHQ.9 < 15)), "/",
             length(which(phq9_subset$PHQ.9 >= 15 & phq9_subset$PHQ.9 < 20)), "/",
             length(which(phq9_subset$PHQ.9 >= 20)))) #n = 261

#both phq2 and 9

num_both_phq2_and_9 <- length(which(!is.na(overlap_group$PHQ.2) & !is.na(overlap_group$PHQ.9)))
print(paste0("num people with both phq2 and 9 = ", num_both_phq2_and_9)) #n = 0



#Number of unique EMPIs in phq2/phq9 subsets
unique_phq2_empis <- length(unique(phq2_subset$EMPI)) #n=966
print(paste0("N with phq2 (Unique EMPI) n = ", unique_phq2_empis, " out of ", dim(phq2_subset)[1], "; n - ", length(unique(phq2_subset$EMPI[phq2_subset$PHQ.2 >= 3])), " meeting criteria for depression (PHQ2) >= 3")) #n = 4606

unique_phq9_empis <- length(unique(phq9_subset$EMPI)) #n=76
print(paste0("N with phq9 (Unique EMPI) n = ", unique_phq9_empis, " out of ", dim(phq9_subset)[1], "; noDep/mild/mod/mod-severe/severe = ", 
             length(unique(phq9_subset$EMPI[phq9_subset$PHQ.9 < 5])), "/",
             length(unique(phq9_subset$EMPI[(phq9_subset$PHQ.9 >= 5 & phq9_subset$PHQ.9 < 10)])), "/",
             length(unique(phq9_subset$EMPI[(phq9_subset$PHQ.9 >= 10 & phq9_subset$PHQ.9 < 15)])), "/",
             length(unique(phq9_subset$EMPI[(phq9_subset$PHQ.9 >= 15 & phq9_subset$PHQ.9 < 20)])), "/",
             length(unique(phq9_subset$EMPI[phq9_subset$PHQ.9 >= 20]))))


#### ICD 9/10 for Depression
dep_df <- overlap_group[grep("F3", overlap_group$ICD10),] #n = 2123
num_depression <- dim(dep_df)[1]
unique_empi <- which(unique(overlap_group$EMPI) %in% overlap_group$EMPI) #index of the locations of unique empis; n = 3885
num_unique_EMPI_and_dep <- length(unique(dep_df$EMPI)) #n = 493

print(paste0("N with ICD 9/10 codes for depression = ", num_depression))

print(paste0("N with ICD 9/10 codes for depression and unique EMPI = ", num_unique_EMPI_and_dep, " out of total depressed - ", dim(dep_df)[1]))

##### PHQ2 or 9 + ICD 9/10 Depression
num_phq2_and_dep <- length(which(!is.na(dep_df$PHQ.2))) #n = 960
print(paste0("N with ICD 9/10 codes for depression and phq2 (ALL SCANS) = ", num_phq2_and_dep, " out of ", dim(dep_df)[1]))

num_phq9_and_dep <- length(which(!is.na(dep_df$PHQ.9))) #n=140
print(paste0("N with ICD 9/10 codes for depression and phq9 (ALL SCANS) = ", num_phq9_and_dep, " out of ", dim(dep_df)[1]))

#phq-2;
print(paste0("N dep + PHQ-2 = ", sum(!is.na(dep_df$PHQ.2)), "; n = ", length(which(dep_df$PHQ.2 >= 3)), " meeting criteria for depression (PHQ2) >= 3")) #n = 4606

#phq-9
print(paste0("N dep + PHQ-9 = ", sum(!is.na(dep_df$PHQ.9)), "; noDep/mild/mod/mod-severe/severe = ", 
             length(which(dep_df$PHQ.9 < 5)), "/",
             length(which(dep_df$PHQ.9 >= 5 & dep_df$PHQ.9 < 10)), "/",
             length(which(dep_df$PHQ.9 >= 10 & dep_df$PHQ.9 < 15)), "/",
             length(which(dep_df$PHQ.9 >= 15 & dep_df$PHQ.9 < 20)), "/",
             length(which(dep_df$PHQ.9 >= 20)))) #n = 261


#### # unique people with dep dx and phq2/9 -> working on this
dep_dx_phq2_unique <- length(unique(dep_df$EMPI[!is.na(dep_df$PHQ.2)])) #n = 201
print(paste0("N with ICD 9/10 codes for depression and phq2 (unique) = ", dep_dx_phq2_unique, " out of ", dim(dep_df)[1]))

dep_dx_phq9_unique <- length(unique(dep_df$EMPI[!is.na(dep_df$PHQ.9)])) #n = 43
print(paste0("N with ICD 9/10 codes for depression and phq9 (unique) = ", dep_dx_phq9_unique, " out of ", dim(dep_df)[1]))

####


#### ICD 9/10 for Healthy Group
healthy_df <- overlap_group[(-grep("F3", overlap_group$ICD10)),] #n = 14707
num_healthy <- dim(healthy_df)[1]
unique_empi <- which(unique(healthy_df$EMPI) %in% healthy_df$EMPI) #index of the locations of unique empis; n = 3244
num_unique_EMPI_and_healthy <- length(unique(healthy_df$EMPI)) #n = 3244

print(paste0("N without Depression/ICD 9/10 codes for healthy = ", num_healthy))

print(paste0("N without Depression/ ICD 9/10 codes for healthy and unique EMPI = ", num_unique_EMPI_and_healthy, " out of ", dim(healthy_df)[1]))

##### PHQ2 or 9 + No Depression ICD9/10
num_phq2_and_healthy <- length(which(!is.na(healthy_df$PHQ.2))) #n = 3646
print(paste0("N without Depression/ ICD 9/10 codes for healthy and phq2 (ALL SCANS) = ", num_phq2_and_healthy, " out of ", dim(healthy_df)[1]))

#phq-2;
print(paste0("N healthy w/PHQ-2 = ", sum(!is.na(healthy_df$PHQ.2)), "; n = ", length(which(healthy_df$PHQ.2 >= 3)), " meeting criteria for depression (PHQ2) >= 3")) #n = 47

num_phq9_and_healthy <- length(which(!is.na(healthy_df$PHQ.9))) #n=121
print(paste0("N without Depression/ ICD 9/10 codes for healthy and phq9 (ALL SCANS) = ", num_phq9_and_healthy, " out of ", dim(healthy_df)[1]))


#phq-9
print(paste0("N healthy w/PHQ-9 = ", sum(!is.na(healthy_df$PHQ.9)), "; noDep/mild/mod/mod-severe/severe = ", 
             length(which(healthy_df$PHQ.9 < 5)), "/",
             length(which(healthy_df$PHQ.9 >= 5 & healthy_df$PHQ.9 < 10)), "/",
             length(which(healthy_df$PHQ.9 >= 10 & healthy_df$PHQ.9 < 15)), "/",
             length(which(healthy_df$PHQ.9 >= 15 & healthy_df$PHQ.9 < 20)), "/",
             length(which(healthy_df$PHQ.9 >= 20)))) #n = 55/34/21/1/10


#### # unique people without dep dx and phq2/9 
dep_dx_phq2_unique <- length(unique(healthy_df$EMPI[!is.na(healthy_df$PHQ.2)])) #n = 201
print(paste0("N without Depression/ ICD 9/10 codes for healthy and phq2 (unique) = ", dep_dx_phq2_unique, " out of ", dim(healthy_df)[1]))

dep_dx_phq9_unique <- length(unique(healthy_df$EMPI[!is.na(healthy_df$PHQ.9)])) #n = 43
print(paste0("N without Depression/ ICD 9/10 codes for healthy and phq9 (unique) = ", dep_dx_phq9_unique, " out of ", dim(healthy_df)[1]))

####

#demographics and lab historgrams
#print histogram of phq-2/9s for people

hist(overlap_group$PHQ.2[which(!is.na(overlap_group$PHQ.2))], main = paste0("PHQ-2 Histo : n = ", length(which(!is.na(overlap_group$PHQ.2)))), xlab = "PHQ-2", breaks = 8)

hist(overlap_group$PHQ.9[which(!is.na(overlap_group$PHQ.9))], main = paste0("PHQ-9 Histo : n = ", length(which(!is.na(overlap_group$PHQ.9)))), xlab = "PHQ-9", breaks = 30)

#fcode histos
hist(dep_df$PHQ.2, main = paste0("PHQ2 and Dep Histo : n = ", num_phq2_and_dep), xlab = paste0("PHQ2"))

hist(dep_df$PHQ.9,main = paste0("PHQ9 and Dep Histo : n = ", num_phq9_and_dep), xlab = paste0("PHQ9"))

###

#age histogram
hist(overlap_group$MRI_ENC_AGE[which(!is.na(overlap_group$MRI_ENC_AGE))], main = paste0("Age Histo : n = ", length(which(!is.na(overlap_group$MRI_ENC_AGE)))), xlab = "AGE AT MRI ENCOUNTER")

#tsh
hist(overlap_group$TSH[which(!is.na(overlap_group$TSH))], main = paste0("TSH Histo : n = ", length(which(!is.na(overlap_group$TSH)))), xlab = "TSH")

#hemoglobin
hist(overlap_group$hemoglobin[which(!is.na(overlap_group$hemoglobin))], main = paste0("Hemoglobin Histo : n = ", length(which(!is.na(overlap_group$hemoglobin)))), xlab = "hemoglobin")

#wbc
hist(overlap_group$WBC[which(!is.na(overlap_group$WBC))], main = paste0("WBC Histo : n = ", length(which(!is.na(overlap_group$WBC)))), xlab = "WBC")

#folate
hist(overlap_group$FOLATE[which(!is.na(overlap_group$FOLATE))], main = paste0("Folate Histo : n = ", length(which(!is.na(overlap_group$FOLATE)))), xlab = "folate", breaks = 10)

#vitamin D
hist(overlap_group$VitD[which(!is.na(overlap_group$VitD))], main = paste0("Vitamin D Histo : n = ", length(which(!is.na(overlap_group$VitD)))), xlab = "Vitamin D", breaks = 10)


#sex
hist(overlap_group$sex_binarized[which(!is.na(overlap_group$sex_binarized))], 
     main = paste0("Sex Histo : n = ", length(which(!is.na(overlap_group$sex_binarized))), "; M = ", length(which(overlap_group$sex_binarized == 1)), "; F = ", length(which(overlap_group$sex_binarized == 2)) ), 
     xlab = "Male = 1, Female = 2", 
     breaks = 2)

#race
hist(overlap_group$race_binarized[which(!is.na(overlap_group$race_binarized))], 
     main = paste0("Race Histo : n = ", length(which(!is.na(overlap_group$race))), "; White = ", length(which(overlap_group$race_binarized == 1)), "; NW = ", length(which(overlap_group$race_binarized == 2))),
     xlab = "white = 1, other = 2", 
     breaks = 2)

#f-codes - people usually have BOTH icd9/10 or neither


```



```{r depression_vs_healthy_melissa_qc_group}

### this chunk can be run separately from the rest of the analysis
### A lot of it is repeat, but I wanted it to be independent
### Started 20211119

homedir <- "/Users/eballer/BBL/msdepression/"
source("~/BBL/msdepression/scripts/msdepression_functions.R")


##########################################################
####                   Prepare the date               ####
##########################################################
#load our df

#from Jan 2021 pull
data <- read.csv("/Users/eballer/BBL/msdepression/data/dac/investigatingdepressioninmspatients_dates_right_format.csv", header = TRUE, stringsAsFactors = FALSE, na.strings = c("NULL"), sep =",")

ms_providers <- c("MARKOWITZ, CLYDE E.", "JACOBS, DINA A.", "WILLIAMSON, ERIC MICHAEL-LEE", "BERGER, JOSEPH ROBERT", "BERGER DO, JOSEPH", "PRUITT, AMY A.", "KOLSON, DENNIS L.", "CHAHIN, SALIM", "NARULA, SONA", "BAR-OR, AMIT")


#keep people with MS providers 
data_empi_acc_f_phq <- data[which(data$Provider %in% ms_providers),] #n = 17067

#keep people with ICD10 code G35 (this is the same # as people with IC9 - 340)
data_empi_acc_f_phq <- data_empi_acc_f_phq[grep("G35", data_empi_acc_f_phq$ICD10),] #n = 16830
table(data_empi_acc_f_phq$Provider)

##########################
### some preprocessing ###
##########################

#make accession # and lab findings into integer type, contained in row 28:42, Margin=2 to work on columns
data_empi_acc_f_phq$ACCESSION_NUM <- as.integer(data_empi_acc_f_phq$ACCESSION_NUM)
data_empi_acc_f_phq[27:29] <- apply(X = data_empi_acc_f_phq[27:29], FUN = as.integer, MARGIN = 2)
data_empi_acc_f_phq[31:45] <- apply(X = data_empi_acc_f_phq[31:45], FUN = as.integer, MARGIN = 2)
data_empi_acc_f_phq$sex_binarized <- ifelse(data_empi_acc_f_phq$SEX == "MALE", 1, 2)
data_empi_acc_f_phq$osex <- ordered(data_empi_acc_f_phq$sex_binarized)
data_empi_acc_f_phq$race_binarized <- ifelse(data_empi_acc_f_phq$RACE == "WHITE", 1, 2)
#get date into better format
data_empi_acc_f_phq$EXAM_DATE <- as.Date(data_empi_acc_f_phq$BEGIN_EXAM_DTTM, format = "%m/%d/%y")
data_empi_acc_f_phq$EXAM_DATE <- as.numeric(gsub(data_empi_acc_f_phq$EXAM_DATE, pattern = "-", replacement = ""))


##########################################################
#### Step 1- make F3* depressed and healthy groups* ######
##########################################################
  ### This is identical to up above, but repeated so I can run this chunk separately

########
### separate out depressed group
########
print("separate out depressed group")
dep_df <- data_empi_acc_f_phq[grep("F3", data_empi_acc_f_phq$ICD10),] #n = 2123
num_depression <- dim(dep_df)[1]
num_unique_EMPI_and_dep <- length(unique(dep_df$EMPI)) #n = 493
print(paste0("N with ICD 9/10 codes for depression = ", num_depression))
print(paste0("N with ICD 9/10 codes for depression and unique EMPI in whole depression group = ", num_unique_EMPI_and_dep, " out of ", num_depression))

#find number of participants who meet criteria for depression in the PHQ2/9 symptom rating
print(paste0("N with ICD 9/10 codes for depression, PHQ2 >= 3, unique = ", length(!is.na(unique(dep_df$EMPI[dep_df$PHQ.2 >= 3])))))
print(paste0("N with ICD 9/10 codes for depression, PHQ9 >= 10, unique = ", length(!is.na(unique(dep_df$EMPI[dep_df$PHQ.9 >= 10])))))


#######
### separate out healthy group
#######
print("separate out healthy group")
healthy_df <- data_empi_acc_f_phq[-grep("F3", data_empi_acc_f_phq$ICD10),] #n = 14707
num_healthy <- dim(healthy_df)[1] 
num_unique_EMPI_and_healthy <- length(unique(healthy_df$EMPI)) #n = 3244
print(paste0("N with WITHOUT depression ICD 9/10 codes (i.e. \"healthy\"): ", num_healthy))
print(paste0("N with WITHOUT ICD 9/10 depression codes for depression and unique EMPI = ", num_unique_EMPI_and_healthy, " out of ", num_healthy))

##########################################################
#### Step 2- Identify PHQ2 >=3 in healthy group     ######
##########################################################

print("Get people in healthy group with phq2s for dep/healthy")
# num in healthy group with PHQ2
phq2_subset <- healthy_df[which(!is.na(healthy_df$PHQ.2)),] #n=3646, unique 698
depressed_phq2_subset <- phq2_subset[which(phq2_subset$PHQ.2 >= 3),] #n = 47 
depressed_unique_phq2_empis <- unique(depressed_phq2_subset$EMPI) #n=10
healthy_phq2_subset <- phq2_subset[which(phq2_subset$PHQ.2 == 0),] #n = 3326
healthy_unique_phq2_empis <- unique(healthy_phq2_subset$EMPI) #n = 631

print(paste0("PHQ2 breakdown in healthy group (total n with score = ", dim(phq2_subset)[1], "[unique = ", length(unique(phq2_subset$EMPI)),"]): PHQ2 >= 3 :", dim(depressed_phq2_subset)[1], "[unique = ", length(depressed_unique_phq2_empis), "]; PHQ2 == 0 : ", dim(healthy_phq2_subset)[1], "[unique = ", length(healthy_unique_phq2_empis),"]"))


##########################################################
#### Step 3- Identify PHQ9 >=10 in healthy group    ######
##########################################################

print("Get people in healthy group with phq9s for dep/healthy")
# num in healthy group with PHQ9
phq9_subset <- healthy_df[which(!is.na(healthy_df$PHQ.9)),] #n=121
depressed_phq9_subset <- phq9_subset[which(phq9_subset$PHQ.9 >= 10),] #n = 32 
depressed_unique_phq9_empis <- unique(depressed_phq9_subset$EMPI) #n=9
healthy_phq9_subset <- phq9_subset[which(phq9_subset$PHQ.9 == 0),] #n = 21
healthy_unique_phq9_empis <- unique(healthy_phq9_subset$EMPI) #n =4

print(paste0("PHQ9 breakdown in healthy group (total n with score = ", dim(phq9_subset)[1], "[unique = ", length(unique(phq9_subset$EMPI)),"]): PHQ9 >= 10 :", dim(depressed_phq9_subset)[1], "[unique = ", length(depressed_unique_phq9_empis), "]; PHQ9 == 0 : ", dim(healthy_phq9_subset)[1], "[unique = ", length(unique(healthy_phq9_subset$EMPI)),"]"))


##########################################################
#Step 4 - Combine for depressed group and healthy groups #
##########################################################

print("Combine groups for new cohort")
gain_in_dep_group <- length(depressed_unique_phq2_empis) + length(depressed_unique_phq9_empis)
dep_num_icd10_plus_phq2_and_phq9 <- num_unique_EMPI_and_dep + gain_in_dep_group # we can do this because we know they are each exclusive - num_unique_empi_and_dep from icd10 group, and no overlap in phq2 and 9 group
print(paste0("number of UNIQUE people with an icd10 code for Depression OR scored positive on PHQ2(>=3) or PHQ9(>=10) : ", dep_num_icd10_plus_phq2_and_phq9, ", for a gain of n = ", gain_in_dep_group))

healthy_num_no_icd10_plus_phq2_and_phq9 <- num_unique_EMPI_and_healthy - gain_in_dep_group #take number of people who don't have depression diagnosis and don't have a depression phq2/9

print(paste0("number of people with NO icd10 code for Depression and NEVER had a PHQ2(>=3) or PHQ9(>=10) : ", healthy_num_no_icd10_plus_phq2_and_phq9, ", for a loss of n = ", gain_in_dep_group))

healthy_num_no_icd10_plus_phq2_and_phq9_MUST_HAVE_PHQ2_OR_9 <- length(healthy_unique_phq2_empis) + length(healthy_unique_phq9_empis)
print(paste0("number of UNIQUE people with NO icd10 code for Depression and HAS HAD AT LEAST 1 PHQ2 or 9 that was 0) : ", healthy_num_no_icd10_plus_phq2_and_phq9_MUST_HAVE_PHQ2_OR_9))


print(paste0("Cleanest cohort (depressed in icd9/10 or Phq2/9; healthy by at least one phq2/9 and never depression dx UNIQUE ---->>>>  Depressed: ", dep_num_icd10_plus_phq2_and_phq9, "; Healthy: ", healthy_num_no_icd10_plus_phq2_and_phq9_MUST_HAVE_PHQ2_OR_9))


##### THESE ARE THE DATAFRAMES I WANT TO USE GOING FORWARD ###
#all empis for depressed group include people with depresssion dx, and people who got in for phq2 or phq9
empis_for_depressed_group <- append(
  append(unique(dep_df$EMPI), depressed_unique_phq2_empis), depressed_unique_phq9_empis)

final_depressed_group_withICD_AND_depressed_phq2_or_9 <- 
  data_empi_acc_f_phq %>%
filter(EMPI %in% empis_for_depressed_group)

#------
empis_for_healthy_group <- append(healthy_unique_phq2_empis, healthy_unique_phq9_empis)

final_healthy_group_withNOICD_AND_phq2_or_9_0<- 
  data_empi_acc_f_phq %>%
filter(EMPI %in% empis_for_healthy_group)

#------
### add a column to the original dataframe with a 0 if not in any group, -1 if healthy, and 1 if depressed
data_empi_acc_f_phq$depGroupVar = 0
data_empi_acc_f_phq$depGroupVar[which(data_empi_acc_f_phq$EMPI %in% empis_for_depressed_group)] = 1
data_empi_acc_f_phq$depGroupVar[which(data_empi_acc_f_phq$EMPI %in% empis_for_healthy_group)] = -1
data_empi_acc_f_phq$depGroupVar = as.factor(data_empi_acc_f_phq$depGroupVar)



##########################################################
#             Step 5 - Read in Fascicle info             #
##########################################################

fascicle_proportions <- read.csv(paste0(homedir, "/results/fascicle_volumes_all_subjects_roi_n2336.csv"), header = T, sep = ",") #n = 2336

#fascicle names are contained in all but the first 2 columns of the fascicle_proportions df
fascicle_names <- names(fascicle_proportions[3:dim(fascicle_proportions)[2]])

#fascicle_mapping, returns numerical mapping as well as names of tracts
fascicle_bundle_mapping <- get_fascicle_bundle_mapping()
##########################################################
#             Step 6 - Merge with data_empi              #
##########################################################
df_demo_and_fascicles <- merge(data_empi_acc_f_phq, fascicle_proportions, by = c("EMPI", "EXAM_DATE")) #n = 2962


##########################################################
#                 Step 7 - Histos                        #
##########################################################
##### Histograms for PHQ2/9 healthy and depressed

hist(df_demo_and_fascicles$PHQ.2[which(!is.na(df_demo_and_fascicles$PHQ.2))], main = paste0("PHQ-2 In Good Mimosa Group : n = ", length(which(!is.na(df_demo_and_fascicles$PHQ.2)))), xlab = "PHQ-2", breaks = 8)

hist(df_demo_and_fascicles$PHQ.9[which(!is.na(df_demo_and_fascicles$PHQ.9))], main = paste0("PHQ-9 In Good Mimosa Group : n = ", length(which(!is.na(df_demo_and_fascicles$PHQ.9)))), xlab = "PHQ-9", breaks = 8) 

hist(df_demo_and_fascicles$PHQ.2[which(!is.na(df_demo_and_fascicles$PHQ.2) & (df_demo_and_fascicles$depGroupVar == 1))], main = paste0("PHQ-2/Depressed In Good Mimosa Group : n = ", length(which(!is.na(df_demo_and_fascicles$PHQ.2) & df_demo_and_fascicles$depGroupVar == 1))), xlab = "PHQ-2", breaks = 8)

hist(df_demo_and_fascicles$PHQ.9[which(!is.na(df_demo_and_fascicles$PHQ.9) & (df_demo_and_fascicles$depGroupVar == 1))], main = paste0("PHQ-9/Depressed In Good Mimosa Group : n = ", length(which(!is.na(df_demo_and_fascicles$PHQ.9) & df_demo_and_fascicles$depGroupVar == 1))), xlab = "PHQ-9", breaks = 8)

hist(df_demo_and_fascicles$PHQ.2[which(!is.na(df_demo_and_fascicles$PHQ.2) & (df_demo_and_fascicles$depGroupVar == -1))], main = paste0("PHQ-2/Healthy In Good Mimosa Group : n = ", length(which(!is.na(df_demo_and_fascicles$PHQ.2) & df_demo_and_fascicles$depGroupVar == -1))), xlab = "PHQ-2", breaks = 8)

hist(df_demo_and_fascicles$PHQ.9[which(!is.na(df_demo_and_fascicles$PHQ.9) & (df_demo_and_fascicles$depGroupVar == -1))], main = paste0("PHQ-9/Healthy In Good Mimosa Group : n = ", length(which(!is.na(df_demo_and_fascicles$PHQ.9) & df_demo_and_fascicles$depGroupVar == -1))), xlab = "PHQ-9", breaks = 8)


##########################################################
#                Step 8 - Regressions                    #
##########################################################

```

```{r dep_vs_healthy_regressions}

#isolate out only the depressed group and healthy group
dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles[df_demo_and_fascicles$depGroupVar != 0,] #n depressed = 393, healthy = 713, total n = 1106

#lm
fascicle_lm <- lapply(fascicle_names, function(x) 
{
  lm(substitute(i ~ depGroupVar, list(i = as.name(x))), data = dep_and_healthy_groups_for_ICD_analysis)
})
names(fascicle_lm) <- fascicle_names

#anova
fascicle_anova <- lapply(fascicle_lm, anova)

#fdr corrected
fascicle_anova_fdr <- fdr_anova_generic(fascicle_anova, 1)
print(fascicle_anova_fdr)

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_anova[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr_association)


#visreg
sapply(fascicle_lm, visreg)
```


```{r phq2_correlation_fascicles}
#isolate out only the depressed group and healthy group
dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles[df_demo_and_fascicles$depGroupVar != 0,] #n depressed = 393, healthy = 713, total n = 1106

#filter those with phq2
with_phq2 <- dep_and_healthy_groups_for_ICD_analysis %>% filter(!is.na(PHQ.2))

#lm
fascicle_lm <- lapply(fascicle_names, function(x) 
{
  lm(substitute(i ~ PHQ.2, list(i = as.name(x))), data = with_phq2)
})
names(fascicle_lm) <- fascicle_names

#anova
fascicle_anova <- lapply(fascicle_lm, anova)

#fdr corrected
fascicle_anova_fdr <- fdr_anova_generic(fascicle_anova, 1)
print(fascicle_anova_fdr)

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_anova[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr_association)

#uncorrected
fascicle_anova_p <- sapply(fascicle_anova, function(v) v$"Pr(>F)"[1])
fascicle_anova_p05_unc <- as.data.frame(fascicle_anova_p[fascicle_anova_p < 0.05])
print(fascicle_anova_p05_unc)

#visreg
#sapply(fascicle_lm, visreg)
```
```{r phq2_correlation_fascicles_dep}
#isolate out only the depressed group and healthy group
dep_groups_for_ICD_analysis <- df_demo_and_fascicles[df_demo_and_fascicles$depGroupVar == 1,] #n depressed = 393, healthy = 713, total n = 1106

#filter those with phq2
with_phq2_dep <- dep_groups_for_ICD_analysis %>% filter(!is.na(PHQ.2) & PHQ.2 != 0) %>% filter(depGroupVar == 1)

#lm
fascicle_lm <- lapply(fascicle_names, function(x) 
{
  lm(substitute(i ~ PHQ.2, list(i = as.name(x))), data = with_phq2_dep)
})
names(fascicle_lm) <- fascicle_names

#anova
fascicle_anova <- lapply(fascicle_lm, anova)

#fdr corrected
fascicle_anova_fdr <- fdr_anova_generic(fascicle_anova, 1)
print(fascicle_anova_fdr)

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_anova[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr_association)

#uncorrected
fascicle_anova_p <- sapply(fascicle_anova, function(v) v$"Pr(>F)"[1])
fascicle_anova_p05_unc <- as.data.frame(fascicle_anova_p[fascicle_anova_p < 0.05])
print(fascicle_anova_p05_unc)

#visreg
#sapply(fascicle_lm, visreg)
```

```{r phq9_correlation_fascicles}
#isolate out only the depressed group and healthy group
dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles[df_demo_and_fascicles$depGroupVar != 0,] #n depressed = 393, healthy = 713, total n = 1106

#filter those with phq2
with_phq9 <- dep_and_healthy_groups_for_ICD_analysis %>% filter(!is.na(PHQ.9))

#lm
fascicle_lm <- lapply(fascicle_names, function(x) 
{
  lm(substitute(i ~ PHQ.9, list(i = as.name(x))), data = with_phq9)
})
names(fascicle_lm) <- fascicle_names

#anova
fascicle_anova <- lapply(fascicle_lm, anova)

#fdr corrected
fascicle_anova_fdr <- fdr_anova_generic(fascicle_anova, 1)
print(fascicle_anova_fdr)

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_anova[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr_association)

#uncorrected
fascicle_anova_p <- sapply(fascicle_anova, function(v) v$"Pr(>F)"[1])
fascicle_anova_p05_unc <- as.data.frame(fascicle_anova_p[fascicle_anova_p < 0.05])
print(fascicle_anova_p05_unc)

#visreg
#sapply(fascicle_lm, visreg)
```
```{r phq9_correlation_fascicles_dep}
#isolate out only the depressed group and healthy group
dep_groups_for_ICD_analysis <- df_demo_and_fascicles[df_demo_and_fascicles$depGroupVar == 1,] #n depressed = 393, healthy = 713, total n = 1106

#filter those with phq2
with_phq9_dep <- dep_groups_for_ICD_analysis %>% filter(!is.na(PHQ.9) & PHQ.9 != 0) 

#lm
fascicle_lm <- lapply(fascicle_names, function(x) 
{
  lm(substitute(i ~ PHQ.9, list(i = as.name(x))), data = with_phq9_dep)
})
names(fascicle_lm) <- fascicle_names

#anova
fascicle_anova <- lapply(fascicle_lm, anova)

#fdr corrected
fascicle_anova_fdr <- fdr_anova_generic(fascicle_anova, 1)
print(fascicle_anova_fdr)

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_anova[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr_association)

#uncorrected
fascicle_anova_p <- sapply(fascicle_anova, function(v) v$"Pr(>F)"[1])
fascicle_anova_p05_unc <- as.data.frame(fascicle_anova_p[fascicle_anova_p < 0.05])
print(fascicle_anova_p05_unc)

#visreg
#sapply(fascicle_lm, visreg)
```

```{r depression_main_effect_unique_subjects}
##### repeat above analysis but use only the first instance of each EMPI, sorted by date
df_unique_empi <- dep_and_healthy_groups_for_ICD_analysis %>% 
  group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice(1) %>% 
  ungroup() #n = 300, 115 depressed, 185 healthy

#lm
fascicle_lm_unique <- lapply(fascicle_names, function(x) 
{
  lm(substitute(i ~ depGroupVar, list(i = as.name(x))), data = df_unique_empi)
})
names(fascicle_lm_unique) <- fascicle_names

#anova
fascicle_anova_unique <- lapply(fascicle_lm_unique, anova)

#fdr corrected
fascicle_anova_unique_fdr <- fdr_anova_generic(fascicle_anova_unique, 1)
print(fascicle_anova_unique_fdr)#anova values < 0.05, uncorrected

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_anova_unique[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr_association)

#uncorrected
fascicle_anova_unique_p <- sapply(fascicle_anova_unique, function(v) v$"Pr(>F)"[1])
fascicle_anova_unique_p05_unc <- as.data.frame(fascicle_anova_unique_p[fascicle_anova_unique_p < 0.05])
print(fascicle_anova_unique_p05_unc)

```
```{r depression_main_effect_mixed_model}
##### repeat above analysis but use only the first instance of each EMPI, sorted by date
df_mm <-df_demo_and_fascicles[df_demo_and_fascicles$depGroupVar != 0,]

#lm
fascicle_lm_mm <- lapply(fascicle_names, function(x) 
{
  lmerTest::lmer(substitute(i ~ depGroupVar + (1 | EMPI), list(i = as.name(x))), data = df_mm)
})
names(fascicle_lm_mm) <- fascicle_names

#anova
fascicle_anova_mm <- lapply(fascicle_lm_mm, anova)

#fdr corrected
fascicle_anova_mm_fdr <- fdr_anova_generic(fascicle_anova_mm, 1)
print(fascicle_anova_mm_fdr)#anova values < 0.05, uncorrected

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_anova_mm[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr_association)

#uncorrected
fascicle_anova_mm_p <- sapply(fascicle_anova_mm, function(v) v$"Pr(>F)"[1])
fascicle_anova_mm_p05_unc <- as.data.frame(fascicle_anova_mm_p[fascicle_anova_mm_p < 0.05])
print(fascicle_anova_mm_p05_unc)

```

```{r age_effects_fascicles}
########### age effect whole group

#isolate out only the depressed group and healthy group
dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles[df_demo_and_fascicles$depGroupVar != 0,] #n depressed = 393, healthy = 713, total n = 1106

#### age histo ###
hist(dep_and_healthy_groups_for_ICD_analysis$PAT_AGE_AT_EXAM,
main = paste0("Age In Good Mimosa Group : n = ", dim(dep_and_healthy_groups_for_ICD_analysis)[1]), xlab = "Age", breaks = 10)

#lm
fascicle_age_lm <- lapply(fascicle_names, function(x) 
{
  lm(substitute(i ~ PAT_AGE_AT_EXAM, list(i = as.name(x))), data = dep_and_healthy_groups_for_ICD_analysis)
})
names(fascicle_age_lm) <- fascicle_names

#anova
fascicle_age_anova <- lapply(fascicle_age_lm, anova)

#fdr corrected
fascicle_age_anova_fdr <- fdr_anova_generic(fascicle_age_anova, 1)
print(fascicle_age_anova_fdr)

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_age_anova[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr_association)

#visreg
#sapply(fascicle_age_lm,visreg)
```

```{r sex_effects_fascicles}
########### sex effect whole group

#isolate out only the depressed group and healthy group
dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles[df_demo_and_fascicles$depGroupVar != 0,] #n depressed = 393, healthhy = 713, total n = 1106

#### sex histo ###
hist(dep_and_healthy_groups_for_ICD_analysis$sex_binarized,
main = paste0("Sex In Good Mimosa Group : n (M/F)= ", sum(dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 1), "/", sum(dep_and_healthy_groups_for_ICD_analysis$sex_binarized == 2)),  xlab = "Sex", breaks = 2)

#lm
fascicle_sex_lm <- lapply(fascicle_names, function(x) 
{
  lm(substitute(i ~ osex, list(i = as.name(x))), data = dep_and_healthy_groups_for_ICD_analysis)
})
names(fascicle_sex_lm) <- fascicle_names

#anova
fascicle_sex_anova <- lapply(fascicle_sex_lm, anova)

#fdr corrected
fascicle_sex_anova_fdr <- fdr_anova_generic(fascicle_sex_anova, 1)
print(fascicle_sex_anova_fdr)

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_sex_anova[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,1)
print(fascicle_anova_fdr_association)

#visreg
#sapply(fascicle_sex_lm,visreg)
```

```{r sex_by_depression_fascicles}
#sex by depression
#isolate out only the depressed group and healthy group
dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles[df_demo_and_fascicles$depGroupVar != 0,] #n depressed = 393, healthhy = 713, total n = 1106

#lm
fascicle_sexdep_lm <- lapply(fascicle_names, function(x) 
{
  lm(substitute(i ~ osex*depGroupVar, list(i = as.name(x))), data = dep_and_healthy_groups_for_ICD_analysis)
})
names(fascicle_sexdep_lm) <- fascicle_names

#anova
fascicle_sexdep_anova <- lapply(fascicle_sexdep_lm, anova)

#fdr corrected
fascicle_sexdep_anova_fdr <- fdr_anova_generic(fascicle_sexdep_anova, 3)
print(fascicle_sexdep_anova_fdr)

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_sexdep_anova[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,3)
print(fascicle_anova_fdr_association)

```
```{r age_by_depression_fascicles}
#sex by depression
#isolate out only the depressed group and healthy group
dep_and_healthy_groups_for_ICD_analysis <- df_demo_and_fascicles[df_demo_and_fascicles$depGroupVar != 0,] #n depressed = 393, healthhy = 713, total n = 1106

#lm
fascicle_agedep_lm <- lapply(fascicle_names, function(x) 
{
  lm(substitute(i ~ PAT_AGE_AT_EXAM*depGroupVar, list(i = as.name(x))), data = dep_and_healthy_groups_for_ICD_analysis)
})
names(fascicle_agedep_lm) <- fascicle_names

#anova
fascicle_agedep_anova <- lapply(fascicle_agedep_lm, anova)

#fdr corrected
fascicle_agedep_anova_fdr <- fdr_anova_generic(fascicle_agedep_anova, 3)
print(fascicle_agedep_anova_fdr)

#fdr corrected only association cortex
fascicle_anova_w_fiber_mapping <- fascicle_agedep_anova[which(fascicle_bundle_mapping$name_vector == "association")]
fascicle_anova_fdr_association <- fdr_anova_generic(fascicle_anova_w_fiber_mapping,3)
print(fascicle_anova_fdr_association)

```


```{r visreg_models}

#visreg
#sapply(fascicle_lm, visreg)
#sapply(fascicle_age_lm, visreg)
#sapply(fascicle_sex_lm, visreg)
#sapply(fascicle_sexdep_lm, visreg)
#sapply(fascicle_lm_unique, visreg)

```

